
\documentclass[11pt]{article}
\usepackage[table]{xcolor}
\usepackage[]{geometry} 
\usepackage{amsmath}
\usepackage{graphicx}

\usepackage{setspace}
\doublespacing

\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{inputenc}

\usepackage{dashrule}
\usepackage{float}
\usepackage{hyperref}
\usepackage{url}
\usepackage{mwe}
\usepackage{caption}

\usepackage[backend=biber,style=ieee]{biblatex}

\addbibresource{D1.bib}

\hypersetup{ linktoc=all}
\graphicspath{ {./images/} }


\begin{document}
\title{%
	\bf Computing at the edge\\ 
	\large Deliverable 1: Final year Dissertation \\
	Bsc Computer Science: Artificial Intelligence}

\author{
	Sam Fay-Hunt | \texttt{sf52@hw.ac.uk}\\
	Supervisor: Rob Stewart | \texttt{R.Stewart@hw.ac.uk}
}

\maketitle

\pagebreak

\textbf{DECLARATION}\\
I, Sam Fay-Hunt confirm that this work submitted for assessment is my own and is expressed in
my own words. Any uses made within it of the works of other authors in any form (e.g., ideas,
equations, figures, text, tables, programs) are properly acknowledged at any point of their
use. A list of the references employed is included.\\
Signed: ......................\\
Date: .........................

\pagebreak

\textbf{Abstract:} a short description of the project and the main work to be carried out – probably
between one and two hundred words
\pagebreak

\tableofcontents
\thispagestyle{empty}
\pagebreak


\setcounter{page}{1}

\section{Introduction}
\emph{\textbf{Summarising the context of the dissertation project, stating the aim and objectives of the project, identifying the problems to be solved to achieve the objectives, and sketching
the organisation of the dissertation.}}

Edge devices have never been cheaper *citation*, stuff about how IoT devices are ubiquitous

Mention how there is an increasing trend to perform computing at the Edge - real time applications + privacy\\
These devices are often equipped with some form of AI application: Photo enhancment ect. Online vs offline learning\\
Edge side inference

These models can have a huge number of parameters

\autocite{chenDeepLearningMobile2020}

Issues with limited resource computation

outline the document: We start with ..., then we cover x, y, and z ...

This dissertation is an investigation into the effect of pruning on inference latency and accuracy with 
hardware without optimisations for processing sparse matrices.

\subsection{Background}
discussing related work found in the technical literature and its relevance to your
project.

Computing at the edge

compression types:\\
pruning\\
distillation\\
Quantization\\


\section{Research Methodology/ Requirements Analysis}
\subsection{Research Methodology}
This is required for research projects and should be linked
back to the project aim and objectives. It should describe the research methods that
will be employed in the project and the research questions that will be investigated.

\subsection{Requirements Analysis}
This is required for technical projects and should be linked
back to the project aim and objectives. It should provide a detailed use case scenario
and suitable use

\section{Design}

\section{Evaluation Strategy}

\section{Project Management}
\subsection{Timetable}

\subsection{Risk Analysis}

\subsection{Professional, Legal \& Ethical issues}

\section{Back matter}
\subsection{References}
listing complete details of all the documents cited in the text
\printbibliography

\subsection{Appendices}
to include additional material, consult with your supervisor.


\end{document}
